Statistical Inference of Transport Mechanisms and Long Time Scale Behavior from Time Series of Solute Trajectories in Nanostructured Membranes.

### 2020-04-03 Ben_Manuscripts/hdphmm/Outline.tex
New script for calculating local density at arbitrary points in unit cell

  \section{Results and Discussion}
  %MRS2: how stable are the results to realizations of the system
  \subsection{Inferring Solute Transport Mechanisms}

  Clustering parameters sets results in X distinct dynamical modes.
  \begin{itemize}
    \item In the figure below, we show time series simulations that qualitatively
    illustrate the difference in dynamical behavior between modes.
  \end{itemize}

  %BJC1: a figure showing some representative fluctuations in each mode

  \noindent We can relate the identified states back to transport mechanisms.
  \begin{itemize}
  	\item More detailed discussion of identified states
  	\item How size of fluctuations, autoregressive parameters are influenced by trapping mechanisms
  	\item How do these states compare to those identified in our previous work?
  	\item Any new states?
  \end{itemize}

  \subsection{Reproducing MD Trajectories and MSDs with the IHMM}

@@

>>>>

  \section{Results and Discussion}

  \subsection{Inferring Solute Transport Mechanisms}

  % BJC: I'll use an example molecule for this section. I'll put files up so
  % that people can look at any trajectory.

  Solutes in this system show a wide range of behavior influenced by the 
  heterogeneity of the nanostructure as well as the interactions between 
  monomers and solute chemical functionality.

  The IHMM does a sufficient job of capturing differences in solute dynamics
  for individual trajectories.
  \begin{itemize}
    \item In Figure TBD, we show the states identified by the IHMM for a single
    methanol trajectory. The IHMM found x number of states, with y of them 
    existing for an appreciable amount of time (quantify this).
  \end{itemize}

  Depending on the path followed, solute trajectories show diverse behavior.
  \begin{itemize}
    \item Some show lots of movement
    \item Some show almost no movement
    \item While all trajectories might not be the same, it is likely that 
    multiple trajectories might share some similar behavior.
  \end{itemize}

  Appropriate clustering helps up group these similarities so that we can 
  more easily interpret the MD trajectories.

  Although we want to narrow the sets of VAR parameters, it is
  important not to prune too much.
  \begin{itemize}
    \item Since we are working with VAR parameters in two dimensions, there
    is a potential for many distinct combinations of behavior.
    \item If we only consider the diagonal entries of the $A$ and $\Sigma$ matrices,
    a total of four independent variables, we can consider clustering each 
    into at least two groups (higher versus lower values), which implies $2^4$ distinct
    dynamical behaviors. 
    %BJC: this might belong in methods
    %BJC: need to come up with a good justification for choice of distance threshold.
    \item If we set the distance threshold too high, visually non-similar states 
    will be clustered together.
    \item If we set the distance threshold too low, we will identify more states 
    than are needed to sufficiently describe the system.
    \item Maybe a plot showing what the trajectories look like with too much clustering. 
  \end{itemize}

  In order to not negelect the large variety of behavior present in this system, we
  aim to strike a balance between clustering and faithfully representing all of
  the types of behavior observed.

  % BJC: Show a trajectory that shares many states with another state. Color them the same to show that clustering did something

  As should be expected, it would be unlikely to expect only a handful of states.
  However, we are well versed in the types of interactions that exist in this system:
  \begin{itemize}
    \item Hydrogen bonding
    \item Sodium Ion association
    \item Distance from pore center
    \item Heterogeneous density
    \item By simultaeneously viewing these metrics alongside state predictions, we 
    can form a picture of how solute's behave in these systems.
    \item And we can determine which of them contribute the most to MSD (?)
  \end{itemize}

  A plot of the different states found and talk about how they are different

  Here are the major observations based on this trajectory.

  Say how this approach is useful and may be best applied carefully on a case by 
  case basis in order to maximize undrestanding. But this is much simpler than
  studying the MD trajectories.

  \subsection{Reproducing MD Trajectories and MSDs with the IHMM}
  % BJC: don't forget to mention in the methods that clustering is necessary in order to
  % construct a single set of parameters used to project MSDs

@@

  More distinct states generally leads to better qualitative matches.
